\textbf{\large Supplementary materials: Development of outdoor air pollution models for estimating exposure in the Barcelona Life Study Cohort (BiSC)}

### 2024-02-19 supplementary_BiSC_outdoor_AP.tex
Updates from Overleaf
finished paper for co-authors

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% --- Tittle of the paper --- %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{\textbf{Supplementary materials: Development of outdoor air pollution models for estimating exposure in the Barcelona Life Study Cohort (BiSC)}}

@@

%%% --- Authors --- %%%
\author{Alan Domínguez, Payam Dadvand, Marta Cirach, Bruno Raimbault, Toni Galmes, Karl Samuelsson, Mark Nieuwenhuijsen, Jordi Sunyer, Xavier Basagaña, Ioar Rivas}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% --- Model development --- %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Model development}

Following the ESCAPE guidelines

@@

%%% --- Table with performance metrics for Hybrid models --- %%%
\begin{table}[ht]
\centering
\begin{threeparttable}
\caption{Performance metric for LUR models.}
\label{Table S3}
\begin{tabular}{llllll}
\toprule
\textbf{Pollutant} & \textbf{Year} & \textbf{N}  &  \textbf{R\textsuperscript{2}\textsubscript{10-CV}} & \textbf{RMSE\textsubscript{10-CV}} & \textbf{Predictor variables}\tnote{1} \\
\midrule
\multirow{2}{*}{NO\textsubscript{2}} & \multirow{2}{*}{2018-2021} & \multirow{2}{*}{489} & \multirow{2}{*}{0.62} & \multirow{2}{*}{4.03} & trafload25 + sqralt + majorroadlength50 + \\ 
 & & & & & roadlength25 + majorroadlength300 \\
\midrule
PM\textsubscript{2.5} & 2019 & 34 & 0.45 & 1.47 & hdres500 + trafnear + ZBE \\
\midrule
BC & 2019 & 30  & 0.83 & 0.18 & hdres50 + linesnear + pop300 + trafload + roads500 \\
\midrule
PM\textsubscript{2.5 - Fe} & 2019 & 34 & 0.89 & 0.03 & trafnear + lat + pop + ZBE  \\
\midrule
PM\textsubscript{2.5 - Cu} & 2019 & 31 & 0.87 & 0.72 & trafnear + roads1000 + ind1000 + pop25 \\
\midrule
PM\textsubscript{2.5 - Zn} & 2019 & 31  & 0.85 & 6.99 & ZBE + roads50 + ind1000 + build25  \\
\bottomrule
\end{tabular}
\begin{tablenotes}
\small
\item[1] Predictor variables (roadlength: total road length (m), majorroadlength: total major road length (m), trafload: total traffic intensity (veh/day), trafnear: traffic intensity at the nearest road (veh/day), linesnear: number traffic lines on nearest street, ZBE: Low Emissions Zone (Yes/No, ref value=No), hdres: high-density residential area (m2), roads: roads surface area (m2), ind: industry area (m2), pop: population density (inhabitants), build: building area (m2), lat: latitude (m), sqralt: squared root altitude (m)).
\end{tablenotes}
\end{threeparttable}
\end{table}

@@

@@

\subsection{Comparison between observed measurements and predictions}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% --- Tittle of the paper --- %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{\textbf{\large Supplementary materials: Development of outdoor air pollution models for estimating exposure in the Barcelona Life Study Cohort (BiSC)}}

@@

%%% --- Authors --- %%%
\author{\small Alan Domínguez, Payam Dadvand, Marta Cirach, Gustavo Arevalo, 
Lluís Barril, María Foraster, Mireia Gascon, Bruno Raimbault, Toni Galmes, Laura Goméz-Herrera, Cecilia Persavento, Karl Samuelsson, Jose Lao, Teresa Moreno, Xavier Querol,
Cathryn Tonne, Mark Nieuwenhuijsen, Jordi Sunyer, Xavier Basagaña, Ioar Rivas}

% --- removing date from manuscript --- % 
\date{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% --- Model development --- %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Model development}
Following the ESCAPE guidelines

@@

\subsection{Validation LUR}
%%% --- Table with performance metrics for Hybrid models --- %%%
\begin{table}[ht]
\centering
\begin{threeparttable}
\caption{Performance metric for LUR models.}
\label{Table S3}
\begin{tabular}{llllll}
\toprule
\textbf{Pollutant} & \textbf{Year} & \textbf{N}  &   \textbf{R\textsuperscript{2}\textsubscript{10-CV}} & \textbf{RMSE\textsubscript{10-CV}} & \textbf{Predictor variables}\tnote{1} \\
\midrule
\multirow{2}{*}{NO\textsubscript{2}} & \multirow{2}{*}{2018-2021} & \multirow{2}{*}{489} & \multirow{2}{*}{0.62} & \multirow{2}{*}{4.03} & trafload25 + sqralt + majorroadlength50 + \\ 
 & & & & & roadlength25 + majorroadlength300 \\
\midrule
PM\textsubscript{2.5} & 2019 & 34 & 0.45 & 1.47 & hdres500 + trafnear + ZBE \\
\midrule
BC & 2019 & 30  & 0.83 & 0.18 & hdres50 + linesnear + pop300 + trafload + roads500 \\
\midrule
PM\textsubscript{2.5 - Fe} & 2019 & 34 & 0.89 & 0.03 & trafnear + lat + pop + ZBE  \\
\midrule
PM\textsubscript{2.5 - Cu} & 2019 & 31 & 0.87 & 0.72 & trafnear + roads1000 + ind1000 + pop25 \\
\midrule
PM\textsubscript{2.5 - Zn} & 2019 & 31  & 0.85 & 6.99 & ZBE + roads50 + ind1000 + build25  \\
\bottomrule
\end{tabular}
\begin{tablenotes}
\small
\item[1] Predictor variables (roadlength: total road length (m), majorroadlength: total major road length (m), trafload: total traffic intensity (veh/day), trafnear: traffic intensity at the nearest road (veh/day), linesnear: number traffic lines on nearest street, ZBE: Low Emissions Zone (Yes/No, ref value=No), hdres: high-density residential area (m2), roads: roads surface area (m2), ind: industry area (m2), pop: population density (inhabitants), build: building area (m2), lat: latitude (m), sqralt: squared root altitude (m)).
\end{tablenotes}
\end{threeparttable}
\end{table}

@@

\subsection{Validaiton LUR: Comparison between measurements and predictions}

@@

\subsection{Validation HM: Comparison between measurements and predictions}
